Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2021-11-18 paper/paper.tex
Changes to automate generation of the chemo manipulations figure
Incorporates tecrot90 gradients figure

The `chemoaffinity only' model begins to encounter problems when we introduce
simulations of experimental manipulations.

% The chemo manipulations figure is made up from 4 figures generated with
% graph_layout::g
%
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_tecrot90_fig4row1.json
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_tecrot180_fig4row2.json
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_tecswap_fig4row3.json
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_mismatch_fig4row4.json
%
\begin{figure}
\includegraphics[width=0.8\linewidth]{./images/fig_chemo_manipulations.png}
\caption{Surgical manipulations in the chemoaffinity-only model. Row A: 90 degree
rotation. Row B: 180 degree rotation. Row C: Graft swap. Row D: mismatch ablation}
\label{f:chsurg}
\end{figure}

>>>>

The `chemoaffinity only' model begins to encounter problems when we introduce
simulations of experimental manipulations. Fig\,\ref{f:chsurg} shows the
results of 6 simulated surgical manipulations. In row A, a patch of tectal
tissue has been cut out and rotated by a quarter turn. This is achieved in
simulation by rotating a square region of the tectal region

% Visualisation of ligand expression and gradients on the tectum for the
% graft-rotate 90 degrees simulated surgical manipulation
\begin{figure}
\includegraphics[width=\linewidth]{./images/Tissuevisb.png}
\caption{Visualisation of ligand expression and gradients on the tectum for the
graft-rotate 90 degrees simulated surgical manipulation}
\label{f:tvrot90}
\end{figure}

% The chemo manipulations figure is made up from 4 figures generated with
% graph_layout::g
%
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_tecrot90_fig4row1.json
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_tecrot180_fig4row2.json
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_tecswap_fig4row3.json
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_retablat_fig4row4.json
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_tecablat_fig4row5.json
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_mismatch_fig4row6.json
%
\begin{figure}
\includegraphics[width=0.8\linewidth]{./images/fig_chemo_manipulations.png}
\caption{Surgical manipulations in the chemoaffinity-only model. Row A: 90 degree
rotation. Row B: 180 degree rotation. Row C: Graft swap. Row D: mismatch ablation}
\label{f:chsurg}
\end{figure}
